A Two-Infall Star Formation History with Outflows and Radial Migration

### 2025-02-20 src/tex/ms.tex

\begin{abstract}
    % The Milky Way's stellar disk can be separated into multiple chemically and kinematically distinct components. 
    The two-infall model has long been proposed to explain the formation of the Milky Way's thick and thin disks through two consecutive gas accretion epochs. It has successfully reproduced observed abundance patterns in the Solar neighborhood and across the disk. However, few studies have explored a two-infall with significant mass-loaded outflows
\end{abstract}

>>>>

\begin{abstract}
    The two-infall model has long been proposed to explain the formation of the Milky Way's thick and thin disks through two consecutive gas accretion episodes. It has successfully reproduced observed abundance patterns such as the [$\alpha$/Fe]-bimodality in the Solar neighborhood and across the disk. However, few studies have explored a two-infall model with significant mass-loaded outflows, nor compared model results with comprehensive age--abundance data across the disk. We run multi-zone galactic chemical evolution (GCE) models with a two-infall star formation history, radially-dependent mass-loaded outflows, and a prescription for radial migration of stellar populations. We compare our model results to abundance patterns across the disk from the Apache Point Observatory Galactic Evolution Experiment (APOGEE) data release 17, supplemented with stellar age estimates using multiple methods. We find that the two-infall model struggles to reproduce all the observed characteristics of the chemical thin disk. Models with low nucleosynthetic yields and outflows experience long-lasting dilution of the gas-phase metallicity which contradicts the local age--metallicity relation. Conversely, models with higher yields and outflows fail to reproduce stellar [$\alpha$/Fe] distributions across the disk \todo{(should I be more specific?)}. These issues can be mitigated, but not completely solved, by enriching the accreted gas to low metallicity. 
\end{abstract}
